---
title: "Homework6"
author: "Tianqi Wang"
date: "10/3/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(message = F)
knitr::opts_chunk$set(warning = F)
knitr::opts_chunk$set(tidy.opts = list(width.cutoff = 60), tidy = TRUE)
knitr::opts_chunk$set(fig.align = 'center') 
options(scipen=999)
library(tidyverse)
library(scales)
library(lmtest)
library(sandwich)
library(knitr)
library(MASS)
library(tseries)
library(car)
```

## Question 1
```{r}
data1 <- read.csv('Myopia.csv')
```

#### (a)
```{r}
xtabs(~ MYOPIC + MOMMY, data = data1)
```

From the cross-table of variable `MYOPIC` and `MOMMY`, we can observe that the percentage the student has myopia would increase a lot if his or her mother had myopia. So I think there is a positive relationship between whether or not a child has myopia and whether or not his or her mother had myopia.

#### (b)
```{r}
model1 <- glm(MYOPIC~MOMMY+DADMY+SPORTHR+READHR+COMPHR+STUDYHR+TVHR+GENDER, family = binomial, data = data1)
summary(model1)
```

From the regression result, the coefficient of the variable `DADMY` is statitically significantly differenet from zero, at significance level $\alpha = 0.01$ and it is positive, which means there is a significant positive relationship between the variable `DADMY` and predicted variable. The coefficient is `0.98824`, which means for those students whose father are myopic, their odds would be `exp(0.9884)-1=``r percent(exp(0.9884)-1)` higher than those whose father are not myoptic，on average, else being equal.

#### (c)
 - **Why are there eight degrees of freedom?**  
    Because there are eight predictor variables, so compare to the base regression model 
 - What is the null hypothesis associated with it?  
    $\beta_{MOMMY} = \beta_{DADMY} = \beta_{SPORTHR} = \beta_{READHR} = \beta_{COMPHR} = \beta_{STUDYHR} = \beta_{TVHR} = \beta_{GENDER} = 0$
 - Where did the test statistic come from?   
    
 - What do you do with the null hypothesis in light of the the test statistic?